A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Beam Dynamics

### 2018-07-10 paper/theor-experiment.tex
more info on time step scan

\subsection{Tests}
Before running a full scale optimization of the problem described in \ref{awaproblem}, 
several computational settings, and 
\subsubsection{Time Step Scan} \label{awa:subsection:test}
A study on time step and 
number of particles was done to reduce the time to simulation while 
maintaining the physics of interest. 
The grid size $16 \times 16 \times 32$ was chosen, 
and parallelized in the x and y directions.
After comparing several options we choose ten thousand particles 
in combination with adjusting the time step (dT) near sensitive elements 
(i.e. quadurpoles, kicker). 
The resulting simulations are low fidelity, but closely approximate 
the mid fidelity simulations for metrics of interest, as shown in 
Fig. \ref{tstep}. For all models, the longitudinal parameters (rms$_s$ and energy) 
are calculated correctly, but we see discrepancies in the transverse 
rms$_x$ and $\epsilon_x$ in the low fidelity results. The
average run time of each simulation with the adjusted time steps was 1.6~minutes.
In comparison the mid fidelity simulations ran for 18~minutes.
%A summary of the parameters used is listed in Table \ref{fidelity}.

@@

>>>>

\subsubsection{Time Step Scan} \label{awa:subsection:test}
Before running a full scale optimization of the problem described in \ref{awaproblem}, 
a study on time step and number of particles in the simulation model 
was done to reduce the time to simulation while 
maintaining the physics of interest. 
The grid size $16 \times 16 \times 32$ was chosen, 
and parallelized in the x and y directions.
After comparing several options (1,000, 10,000, 20,000, 50,000, 100,000) 
with a small time step, the number of particles was fixed at ten thousand.
Next several time steps were explored, see Table~\ref{timestep}.
The largest steps were too big to resolve the physics needed.
See low fidelity plot in Fig.~\ref{tstep} for $dT=$\num{5E-11} results.  
In the drifts and linac tanks, \num{1E-11} was sufficient, 
but still not acceptable near the quadrupoles.

in combination with adjusting the time step (dT) near sensitive elements 
(i.e. quadurpoles, kicker, septum). 
The resulting simulations are low fidelity, but closely approximate 
the mid fidelity simulations for metrics of interest, as shown in 
Fig.~\ref{tstep}. For all models, the longitudinal parameters (rms$_s$ and energy) 
are calculated correctly, but we see discrepancies in the transverse 
(rms$_x$ and $\epsilon_x$) for low fidelity results. This discrepancy is 
what led to The
average run time of each simulation with the adjusted time steps was 1.6~minutes.
In comparison the mid fidelity simulations ran for 18~minutes.
Note, a smaller time step, \num{1E-13}, is always used in the gun where the 
beam is low energy and changing rapidly.
%A summary of the parameters used is listed in Table \ref{fidelity}.

@@

\begin{table}%[h!]
	\begin{center}
		\caption{Checkmarks (\cmark) indicate desired physics is resolved. 
			An (\xmark) indicates the time step is too large.}
		\label{timestep}
		\begin{tabular*}{0.6\textwidth}{c c c c }
			\hline\noalign{\smallskip}
			Time Step (dT) & Linac & Drift & Quadrupoles \\
			\noalign{\smallskip}\hline\noalign{\smallskip}
			$5 \times10^{-10}$  & \xmark & \xmark & \xmark \\
			$1 \times10^{-10}$  & \xmark & \xmark & \xmark \\
			$5 \times10^{-11}$  & \xmark & \xmark & \xmark \\
			$1 \times10^{-11}$  & \cmark & \cmark & \xmark \\
			$5 \times10^{-12}$  & \cmark & \cmark & \xmark \\
			$1 \times10^{-12}$  & \cmark & \cmark & \cmark \\
			\noalign{\smallskip}\hline
		\end{tabular*}
	\end{center}
\end{table}
